### 2024-03-29 doc/sections/introduction.tex
[ tex ] Conclusions and Future Work, and some small fixes

The technique of cut-elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for bunched implications.

>>>>

The technique of cut-elimination by construction of a semantic model for MALL is due to Okada~\cite{Okada99:psc}, who shows that the phase space model of MALL, described by Girard~\cite[\S4.1]{Girard87:ll} and Troelstra~\cite[\C8]{Troelstra92:lll}, can be constructed from cut-free proofs.
The completeness of this model directly yields the existence of a cut-free proof for every proof constructible in the MALL sequent calculus.
The same technique was used by Abrusci~\cite{Abrusci91:psc} for non-commutative linear logic, by De, Jafarrahmani, and Saurin~\cite{De22:psc} for MALL with fixed points, and by Frumin~\cite{Frumin22:psc} for Bunched Implications.

### 2024-03-29 doc/sections/mav-extensions.tex
[ tex ] title, grant ack, and small fixes
[ tex ] Conclusions and Future Work, and some small fixes

\section{Extensions}\label{sec:mav-extensions}

\subsection{Additive Units}

\subsection{Multiplicative-Additive Linear Logic}

\subsection{Display Calculus}

Cut-elimination for a Display calculus?

>>>>

\section{Conclusions and Future Work}\label{sec:future-work}

We have presented semantic proof of generalised Cut elimination for
the Multiplicative-Additive System Virtual (MAV), reducing Horne's
approximately 41 page proof to 7 and also providing an Agda
mechanisation. Our proof technique also restricts easily to BV (we
simply skip the use of $+$-closed lower sets and use lower sets
directly instead). We believe that adding additive units ($\top$ and
$0$ in Girard's notation) will be straightforward.

This work opens up several paths for future work. The theory developed
here for lifting Day pomonoids to $+$-closed lower sets should also
enable alternative Cut-elimination proofs for other substructural
logics, such as MALL and Bunched Implications (Okada's technique has
already been applied here by Frumin \cite{Frumin22:psc}). We find the
technique of using $+$-closed lower sets rather than more opaque
closure operators more revealing in how the

We also plan to investigate extensions of MAV with exponentials, as in
the System NEL \cite{GuglielmiS11}, and Kleene Star operators which
can be seen as the exponential for the $\vSeq$ connective. Adding a
Kleene Star would tighten the connection with Concurrent Kleene
Algebras we highlighted in \Cref{remark:cka}. More generally, fixpoint
operators following Baelde \cite{Baelde12} and De, Jafarrahmani and
Saurin \cite{De22:psc}. The latters' use of Okada's technique is not
compatible with Agda's logic because it relies on impredicativity to
construct fixpoints with the double negation closure. We believe that
our more direct predicative technique will be able to use Agda's
inductive and coinductive types.

We also plan to extend our semantics of BV and MAV to a categorical
semantics that considers equalities between proofs as well as
provability. Such a semantics ought to be useful for treating MAV as a
session-types style language, as considered by Ciobanu and Horne
\cite{Ciobanu_2016}. The necessary analogue of MAV-algebras has
already been investigated by Blute, Panangaden and Slavnov
\cite{Blute_2010} as BV-categories, which are Aguiar and Mahajan's
2-monoidal, or duoidal, categories \cite{Aguiar_2010} extended with
duality. The key task will be to categorify the constructions in this
paper to show how the categorical analogue of MAV-frames induces
MAV-categories.

### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] Conclusions and Future Work, and some small fixes

\begin{remark}
  MAV-frames (and MAV-algebras) are also very similar to the
  definition of a \emph{Concurrent Kleene Algebra} (CKA) due to Hoare,
  M{\"o}ller, Struth and Wehrman \cite[Definition
  4.1]{HoareMSW09}. One difference is that we do not assume that $+$
  is a join, nor do we assume the existence of infinitary
  joins. Consequently, we have no analogue of the Kleene Star. Another
  difference is that the duoidal relationship is reversed in
  MAV-frames, indicating that MAV-frames capture evolution of
  processes while MAV-algebras and CKA capture properties of
  processes.
\end{remark}

\begin{proposition}\label[prop]{prop:nmav-frame}
  The \emph{normal proof MAV-frame} \NMAV is the partial order arising
  as the quotient of the preorder formed from the structures of MAV and
  $\vP\leq\vQ$ if there is a normal derivation $\vP\vInferFrom*\vQ$,
  defined as $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$,
  where $\vSS$ is the set of all MAV structures.
  The required (in)equalities follow directly from the definition of $\longrightarrow^*$.
\end{proposition}

>>>>

\begin{remark}\label[remark]{remark:cka}
  MAV-frames (and MAV-algebras) are also very similar to the
  definition of a \emph{Concurrent Kleene Algebra} (CKA) due to Hoare,
  M{\"o}ller, Struth and Wehrman \cite[Definition
  4.1]{Hoare_2011}. One difference is that we do not assume that $+$
  is a join, nor do we assume the existence of infinitary
  joins. Consequently, we have no analogue of the Kleene Star. Another
  difference is that the duoidal relationship is reversed in
  MAV-frames, indicating that MAV-frames capture evolution of
  processes while MAV-algebras and CKA capture properties of
  processes.
\end{remark}

\begin{proposition}\label[prop]{prop:nmav-frame}
  The \emph{normal proof MAV-frame} \NMAV is the partial order arising
  as the quotient of the preorder formed from the structures of MAV
  and $\vP\leq\vQ$ if there is a normal derivation
  $\vP\vInferFrom*\vQ$, defined as
  $(\vSS, \vInferFrom*, \vParr, \vSeq, \vUnit, \vWith)$, where $\vSS$
  is the set of all MAV structures.  The required (in)equalities
  follow directly from the definition of $\vInferFrom*$ for normal
  proofs.
\end{proposition}
